---
title: "CEOs Photos and other Voluntary Disclosure on Shareholder letters"
author: "Anh Dang"
date: "4/24/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### What is a shareholder letter? 
Shareholder letters are letters composed by the CEOs or Chairs of the board. The letters are normally attached to the Annual financial reports and delivered to the shareholder every year-end.
Although the shareholder letter is an important chanel for CEOs to communicate with the company investors, this important piece of document is not required to be filed with the SEC.Since the letter is composed by the top executives themselves, it could reflect many insights about the firm past operation or the CEO’s projection of the future for the firms.

* The letter can be very short and act like an invitation for shareholders to come to the annual shareholder meetings.
  + This is an example of a [very short shareholders letter](https://github.com/anhdang94/Shiny-app-final-project/blob/master/Examples/Chase%20shareholders%20letter.png) from JP Morgan Chase.
 
* The letter can also be very long and full of additional financial information to either summarizing prior year performance or promising future performance.
  + This is an example of a [very elaborated shareholders letter](https://github.com/anhdang94/Shiny-app-final-project/blob/master/Examples/Delta%20Airline%20shareholders%20letter.png) from Delta Airline


As you can see in the two very opposite examples above, the letter from Chase's CEO is quite "bare" and contain no valuable information at all. In opposite the letter from Delta's CEO are very meticulous and full of financial information. Delta's letter also have a nice photo of their CEO attached.



### Question to consider
*  __Why are there companies ,like Delta Airline, who try to include so much financial info and even a photo of their CEO into the shareholder letters?__  Notice that all of the financial info is reported officially in the annual reports (10-K) already. 


*  __Why are there companies, such as Chase, who discuss no finanacial info and attach no CEO photos at all?__  

Combine the two questions above, we have a more general research question as follow:

*__Why do companies include their CEO photos and other financial information within their shareholder letters?__*



### Theories

* Photos can promote trustworthiness and transparency

* Additional financial/operational information can highlight important past year good accomplishment and strengthen investors trust in firm’s performance

* Additional information can also soften bad impression of investors about prior year poor performance through positive future forecast.

* Since the shareholder letter is brief and normally attached at top of financial reports, it act as the tool for executives can use to create the first impression with shareholders

* Main hypothesis: __A firm’s decision to include executive photos and additional information in the shareholder letters is influenced by its current financial status.__



### Initial observation
As seen in the boxplots below, when the financial performance of the firm is good (which is indicated by higher Net Income, higher Revenue, etc.), the CEO is more likely to include his photos or additional financial information with in the shareholder letter. 

We can have a feeling now that the CEOs do not just simply include his photos and other financial information just for asthetic purpose.



```{r shletters, echo=FALSE}
#Load the Library
library(shiny)
library(ggplot2)
library(tidyverse)
library(RCurl)

load(url("https://raw.githubusercontent.com/anhdang94/Shiny-app-final-project/master/Sharehoders_letter_part1.RData"))

# Define UI for application 
ui <- fluidPage(
  
  # Application title
  titlePanel("Different financial statements elements interaction with shareholder letter elements"),
  
  # Sidebar layout
  sidebarLayout(
    #Inputs: Select which inputs from the data we want to display
    sidebarPanel(
      #Select variable for y-axis
      selectInput(inputId = "y", 
                  label = "Element of financial statements",
                  choices = c("Net_Income","Revenue","Year_end_stock_price","EPS"), 
                  selected = "Net_Income"),
      #Select X-axix variables
      selectInput(inputId = "x", 
                  label = "Element of shareholder letters:",
                  choices = c("Shareholders_Letter", "CEO_photo", "Other_Financial_info"), 
                  selected = "Shareholders_Letter"),

    ),
    
    #Output: Type of plot
    mainPanel(
      plotOutput(outputId = "ScatterPlot") 
    )
  )
)

# Define server logic required to draw a scatter plot
server <- function(input, output) {
  
  output$ScatterPlot <- renderPlot({
    # draw the scatter plot
    ggplot(shletter, aes_string(x=input$x, y=input$y,color=input$x)) + geom_boxplot() #Notice the difference between the ggplots
  })
}
# Run the application 
shinyApp(ui = ui, server = server)

```


### Regression


```{r regression, echo=FALSE}


```





